---
title: "R Markdown Example"
author: "Nathaniel E. Helwig"
date: "January 16, 2017"
output: pdf_document
---

This is how you write basic math inline with text:  $x + y = z$  \

\bigskip

This is how you write basic math in displayed equation:
\[
x + y = z
\]

\bigskip

This is how you write a matrix:
\[
\mathbf{X} = 
\left(
\begin{matrix} 
x_{11} & x_{12} & x_{13} \\
x_{21} & x_{22} & x_{23} \\
\end{matrix}
\right)
\]

\bigskip

This is how you make a numbered list:
\begin{enumerate}
\item First element of list
\item Second element of list
\end{enumerate}

\bigskip

This is how you make an unnumbered list:
\begin{itemize}
\item First element of list
\item Second element of list
\end{itemize}

\bigskip 

This is how you include basic R code:
```{r}
set.seed(1)
x = rnorm(1000)
mean(x)
sd(x)

y = rnorm(1000,mean=1,sd=2)
mean(y)
sd(y)
```


This is how you include R code with figures (no difference!):
```{r}
set.seed(1)
x = rnorm(1000)
hist(x)
```

\bigskip

This is how you include the value $\pi$ = `r pi` inline with text.

